Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-17 manuscript.Rmd

proQuestBWR.f(csv=FALSE, path=path)
save(proQuestBWR.df, file = "ProQuest.R")
```

@@

ebscoBWR.f(csv=FALSE, path=path)
save(ebscoBWR.df, file = "ebscoFULL.R")
```

>>>>

proQuestBWR.df <- proQuestBWR.f(csv=FALSE, path=path)
save(proQuestBWR.df, file = "ProQuest.R")
```

@@

ebscoBWR.df <- ebscoBWR.f(csv=FALSE, path=path)
save(ebscoBWR.df, file = "ebscoFULL.R")
```
